---
title: "nytimes_clicks"
author: "mcdevitt"
date: "31 mars 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2) # used for visualizations
library(plyr)

```

## NYTimes Click Thru Evaluation


```{r }

home_dir <- "~/_smu/_src/nytimes_clicks"
data_dir <- paste0(home_dir, "/data")
setwd(home_dir)

file_exists <- TRUE

if (file_exists)
{
	load("./data/nytc.Rda")	# ...	load the saved data frame ...
} else {
	fileLocation <- "http://stat.columbia.edu/~rachel/datasets/nyt1.csv"
	df_nytc <- read.csv(url(fileLocation))
	save(df_nytc, file = "./data/nytc.Rda")
}

# Use the section below if you would rather import the data from a local file
# fileLocation <- "~/path/for/the/file/nyt1.csv"
# df_nytc <- read.csv("fileLocation")

# distribution of the Age column
hist(df_nytc$Age, main="", xlab="Age")

# distribution of the Clicks column
hist(df_nytc$Clicks, main="", xlab="# of Clicks")

range(df_nytc$Clicks)

#Create a new variable ageGroup that categorizes age into following groups: 
#< 18, 18–24, 25–34, 35–44, 45–54, 55–64 and 65+.

df_nytc$Age_Group <- cut(df_nytc$Age, c(-Inf, 18, 24, 34, 44, 54, 64, Inf))

levels(df_nytc$Age_Group) <- c("<18", "18-24", "25-34", "35-44", "45-54", "55-64", "65+")
# Name the levels of 'Age_Group' for readability

#Use sub set of data called “ImpSub” where Impressions > 0 ) in your data set.

#Create a new variable called click-through-rate (CTR = click/impression).
#Use this ImpSub data set to do further analysis.

d1 <- df_nytc[(df_nytc$Impressions > 0),]
d1$CTR <- d1$Clicks/d1$Impressions


ggplot(subset(d1, Impressions>0), aes(x=Impressions, fill=Age_Group))+
    geom_histogram(binwidth=1)



```


#Define a new variable to segment users based on click -through-rate (CTR) behavior.
#    CTR< 0.2, 0.2<=CTR <0.4, 0.4<= CTR<0.6, 0.6<=CTR<0.8, CTR>0.8

d1$ctr_counts <- cut(d1$CTR, c(-Inf, 0.2, 0.4, 0.6, 0.8, Inf))

#Get the total number of Male, Impressions, Clicks and Signed_In
#  (0=Female, 1=Male)

dim(d1[d1$Gender == 1,])[1]
dim(d1[d1$Impressions == 1,])[1]
dim(d1[d1$Clicks == 1,])[1]
dim(d1[d1$Signed_In == 1,])[1]

# Get the mean of Age, Impressions, Clicks, CTR and percentage of males and signed_In 

means_all <- sapply(d1, mean)


mean(d1$Age)
mean(d1$Impressions)
mean(d1$Clicks)
mean(d1$CTR)
mean(mean(d1$Gender))
mean(d1$Signed_In)

#Get the means of Impressions, Clicks, CTR and percentage of males and signed_In  by AgeGroup.

mean(d1$Impressions)
mean(d1$Clicks)
mean(d1$CTR)
mean(mean(d1$Gender))
mean(d1$Signed_In)

list_levels <- levels(d1$Age_Group)
means_list <- list()

means_table <- data.frame(matrix(ncol = 6, nrow = 0))
tbl_names <- c("Age_Group, "Age", "Impressions", "Clicks", "CTR", "Signed_In")
colnames(means_table) <- tbl_names

for (ll in 1:length(list_levels))
{
	df_subset <- d1[d1$Age_Group == list_levels[ll],]
	df_sub_subset <- subset (df_subset, select = c(Age, Impressions, Clicks, CTR, Signed_In))
	means_list <- sapply(df_sub_subset, mean)
	
	print(sprintf ("Age Group : %s | Means : ", list_levels[ll]))
	print(sprintf("%8.3f", means_list))
}

#Create a table of CTRGroup vs AgeGroup counts.

attach(d1)
x_table <- count(d1, c("Age_Group","ctr_counts"))
detach(d1)


#Plot distributions of number impressions and click-through-rate (CTR = click/impression) for the age groups

#Plot distributions of number impressions and click-through-rate (CTR = click/impression) for the age groups.

ggplot(subset(d1, CTR>0), aes(x=CTR, fill=Age_Group))+
    labs(title="Click-through rate by age group (05/01/2012)")+
    geom_histogram(binwidth=.025)


#One more plot you think which is important to look at.





#Submit your file (any format) in to Live session Unit 10 Assignment


```
