---
title: "nytimes_clicks"
author: "mcdevitt"
date: "31 mars 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2) # used for visualizations
library(plyr)
library(GGally)


```
  
***  

## NYTimes Click Thru Evaluation  
  
  
* From the data sets at http://stat.columbia.edu/~rachel/datasets/ there are 31 data sets named nyt1.csv, nyt2.csv, ...  
* Each set represents one simulated day's worth of ads shown and click recorded on New York Times home page in May 2012  
* Each row represents one user  
* Five columns represent :
	+ age,
	+ gender (0 = female, 1 = male),
	+ number of impressions,  
	+ number of clicks, and  
	+ whether user logged in.  
  
  
  
***    
#### Read in base data file  

```{r read data file}

home_dir <- "~/_smu/_src/nytimes_clicks"
data_dir <- paste0(home_dir, "/data")
setwd(home_dir)


# ...	toggle file_exists TRUE/FALSE depending on if .Rda file already locally saved

file_exists <- TRUE

if (file_exists)
{
	load("./data/nytc.Rda")	# ...	load the saved data frame ...
} else {
	fileLocation <- "http://stat.columbia.edu/~rachel/datasets/nyt1.csv"
	df_nytc <- read.csv(url(fileLocation))
	save(df_nytc, file = "./data/nytc.Rda")
}
```


***  
#### __distribution of the Age column__  

```{r}

hist(df_nytc$Age, main="Age Distribution", xlab = "Age")

hist(df_nytc[df_nytc$Age > 0,]$Age, main="Age Distribution - Remove 0s", xlab = "Age")

```

***  
#### __distribution and range of the Clicks column__  

```{r}
hist(df_nytc$Clicks, main="", xlab="# of Clicks")

range(df_nytc$Clicks)
```

***  

#### __Create a new variable ageGroup that categorizes age into following groups:__   
#### * < 18, 18–24, 25–34, 35–44, 45–54, 55–64 and 65+.    
##### * Name the levels of 'Age_Group' for readability  

```{r}

df_nytc$Age_Group <- cut(df_nytc$Age, c(-Inf, 18, 24, 34, 44, 54, 64, Inf))

levels(df_nytc$Age_Group) <- c("<18", "18-24", "25-34", "35-44", "45-54", "55-64", "65+")

```


***  
#### __Use sub set of data called “imp_sub” where Impressions > 0 in your data set.__  
####	* Create a new variable called click-through-rate (clk_thru_rate = clicks / impression).  
####	* Use this imp_sub data set to do further analysis.  

```{r}

df_imp_sub <- df_nytc[(df_nytc$Impressions > 0),]
df_imp_sub$clk_thru_rate <- df_imp_sub$Clicks / df_imp_sub$Impressions

```

***  
#### __Plot distributions of number impressions for the age groups__  

```{r}
ggplot(subset(df_imp_sub, Impressions > 0), aes(x = Impressions, fill = Age_Group)) +
	geom_histogram(binwidth = 1)

```
***  
#### __Plot distributions of click-through-rate (clk_thru_rate = click/impression) for the age groups__  


```{r}
ggplot(subset(df_imp_sub, clk_thru_rate > 0), aes(x = clk_thru_rate, fill = Age_Group))+
    labs(title="Click-through rate by age group (05/01/2012)")+
    geom_histogram(binwidth = .02)

```

***  
#### __Define a new variable to segment users based on click-through-rate behavior.__  
####	* clk_thru_rate< 0.2, 0.2<=clk_thru_rate <0.4, 0.4<= clk_thru_rate<0.6, 0.6<=clk_thru_rate<0.8, clk_thru_rate>0.8

```{r}

df_imp_sub$clk_thru_rate_counts <- cut(df_imp_sub$clk_thru_rate, c(-Inf, 0.2, 0.4, 0.6, 0.8, Inf))

```

***  
#### __Get the total number of Male, Impressions, Clicks and Signed_In__  
####	* (0 = Female, 1 = Male)

```{r}

n_males <- dim(df_imp_sub[df_imp_sub$Gender == 1,])[1]
n_imps <- dim(df_imp_sub[df_imp_sub$Impressions == 1,])[1]
n_clicks <- dim(df_imp_sub[df_imp_sub$Clicks == 1,])[1]
n_signed_in <- dim(df_imp_sub[df_imp_sub$Signed_In == 1,])[1]

```

```{r, cat block, echo = FALSE}

cat ("Number of males       = ", n_males)
cat ("Number of impressions = ", n_imps)
cat ("Number of clicks      = ", n_clicks)
cat ("Number of signed in   = ", n_signed_in)

```

***  
#### __Get the mean of Age, Impressions, Clicks, clk_thru_rate and percentage of males and signed_In__  

```{r}

col_drops <- c("Age_Group", "clk_thru_rate_counts")
df_imp_sub_tmp <- df_imp_sub[ , !(names(df_imp_sub) %in% col_drops)]

means_all <- sapply(df_imp_sub_tmp, mean)

means_all

```

***  
#### Get the means of Impressions, Clicks, clk_thru_rate and percentage of males and signed_In __by AgeGroup.__  

```{r}

df_imp_sub <- df_imp_sub[c(1:5,7,6,8)]

aggregate(df_imp_sub[, 1:6], list(df_imp_sub$Age_Group), mean)

```

***  
#### __Create a table of clk_thru_rate Group vs Age Group counts.__  

```{r}

x_table <- ddply(df_imp_sub, .(df_imp_sub$clk_thru_rate_counts, df_imp_sub$Age_Group), nrow)
names(x_table) <- c("Clk Thru Rate Group", "Age Group", "Freq")

x_table

```


#### __One more plot you think which is important to look at.__  

* this is based on plot explanation from :  
	+ https://www.r-bloggers.com/example-9-17-much-better-pairs-plots/

```{r}

ggpairs(df_exp_plot,
		columns = c("clk_thru_rate_counts", "Age_Group", "Gender"),
	    diag = list(continuous = "density", discrete = "bar"), axisLabels = "show")

```
  

***   
 ... end_of_file  
***  
  
  
